Modelling potential environmental impacts of science activity in Antarctica

### 2025-10-08 talk/index-2.qmd
added light colour themed version

---
title: "Modelling potential environmental impacts of science activity in Antarctica"
title-slide-attributes:
    data-background-image: background-image.png
    data-background-opacity: "0.65"
author: 
  - name: David O'Sullivan
    affiliations: 
      - name: Geospatial Stuff
      - name: University of Auckland
  - name: Fraser Morgan
    affiliations: 
      - name: Bioeconomy Science Institute
format:
  revealjs:
    theme: [black, custom.scss]
    transition: none
    navigation-mode: vertical
    fragment-in-url: true
    slide-number: false
    logo: logo.png
    footer: "Palmerston North Regional GIS Forum, September 2025"
    self-contained: false
---

## Overview {.smaller background-image="miers-valley.jpg"}
### [Study area and data](#study-area-and-data-1)
### [Hiking networks](#hiking-networks-1)
### [Some outputs](#some-outputs-1)
### [Conclusions](#conclusions-1)

@@

##
![](fig-study-area-1.png){width="80%" fig-align="center"}

![](north-arrows.png){.absolute top=65 left=177 width="200" .fragment .fade-in-then-out}

@@

get_graph_plot <- function(G, main, crs = 2193) {
  return(ggplot() +
    geom_sf(data = G |> get_graph_as_line_layer(crs = 2193),
            lwd = 1, colour = "grey") +
    geom_sf(data = G |> vertex_attr() |> as.data.frame() |> 
              st_as_sf(coords = 1:2, crs = crs), size = 12,
              colour = "#191919", fill = "grey", shape = 21) +
    coord_sf(xlim = c(-270, 270) + 1e6, 
             ylim = c(-270, 270) + 1e6, expand = FALSE) +
    ggtitle(main)) +
    theme(
      plot.background = element_rect(fill = "#191919"),
    )
}

@@

wrap_plots(ggplots, nrow = 1) & theme(
  plot.background = element_rect(fill = "#191919"),
  text = element_text(colour = "white")
)
```

@@

## Up $\neq$ down {background-image="klondike.jpg" background-opacity="0.65"}
### Slope is critical to movement, so attach heights to nodes and calculate slope in each direction along lattice edges
### Then use a *hiking function* to estimate traversal times

@@

![](fig-betweenness-map-1.png){fig-align="center"}

@@

![](fig-radius-limited-betweenness-1.png){fig-align="center"}

@@

![](fig-betweenness-limited-sites-1.png){fig-align="center"}

@@

![](fig-approx-minimum-arborescence-1.png){fig-align="center"}

# Conclusions {.smaller background-image="beacon-valley.jpg"}

@@

::: {style="text-shadow:0px 0px 8px rgba(102,0,0,0.35),0px 0px 4px rgba(102,0,0,0.65);background-color:rgba(102,0,0,0.1);backdrop-filter:blur(2px);padding:5px;border-radius:5px;"}
### Hiking network concept is implicit in hiking functions but a new terrain representation
### Terrain-differentiated GPS data-fitted hiking functions are novel {.fragment}
### Potential wider application of radius-limited betweenness centrality {.fragment}
### Next up: start a conversation with Antarctic scientists about planning {.fragment}
:::

@@

::: {style="background-color:rgba(102,0,0,0.1);backdrop-filter:blur(2px);padding:5px;border-radius:5px;"}
<h2 style="text-align:center;text-shadow:0px 0px 8px rgba(102,0,0,0.35),0px 0px 4px rgba(102,0,0,0.65);">For more</h2>
### On this project [dosull.github.io/antarctica](https://dosull.github.io/antarctica) {style="text-align:center;text-shadow:0px 0px 8px rgba(102,0,0,0.35),0px 0px 4px rgba(102,0,0,0.65);"}
### On ![](logo.png){style="vertical-align:middle;width:60px;text-align:center;"} Geospatial Stuff [dosull.github.io](https://dosull.github.io) {style="text-align:center;text-shadow:0px 0px 8px rgba(102,0,0,0.35),0px 0px 4px rgba(102,0,0,0.65);"}
:::

>>>>

---
title: "Modelling potential environmental impacts of science activity in Antarctica"
title-slide-attributes:
    data-background-image: background-image.png
    data-background-opacity: "0.65"
author: 
  - name: David O'Sullivan
    affiliations: 
      - name: Geospatial Stuff
      - name: University of Auckland
  - name: Fraser Morgan
    affiliations: 
      - name: Bioeconomy Science Institute
format:
  revealjs:
    theme: [white, custom.scss]
    transition: none
    navigation-mode: vertical
    fragment-in-url: true
    slide-number: false
    logo: logo.png
    footer: "Palmerston North Regional GIS Forum, September 2025"
    self-contained: false
---

## Overview {.smaller background-image="miers-valley.jpg"}
::: {style="background-color:rgba(0,51,102,0.5);border-radius:5px;padding:5px;width:42%;text-shadow:0px 0px 3px white;"}
### [Study area and data](#study-area-and-data-1)
### [Hiking networks](#hiking-networks-1)
### [Some outputs](#some-outputs-1)
### [Conclusions](#conclusions-1)
:::

@@

##
![](fig-study-area-2.png){width="80%" fig-align="center"}

![](north-arrows.png){.absolute top=65 left=179 width="200" .fragment .fade-in-then-out}

@@

get_graph_plot <- function(G, main, crs = 2193) {
  return(ggplot() +
    geom_sf(data = G |> get_graph_as_line_layer(crs = 2193),
            lwd = 1, colour = "darkgrey") +
    geom_sf(data = G |> vertex_attr() |> as.data.frame() |> 
              st_as_sf(coords = 1:2, crs = crs), size = 12,
              colour = "white", fill = "darkgrey", shape = 21) +
    coord_sf(xlim = c(-270, 270) + 1e6, 
             ylim = c(-270, 270) + 1e6, expand = FALSE) +
    ggtitle(main) +
    theme(
      plot.background = element_rect(fill = "white"),
    ))
}

@@

wrap_plots(ggplots, nrow = 1) & theme(
  plot.background = element_rect(fill = "white", colour = NA),
  text = element_text(colour = "black")
)
```

@@

## Up &#8800; down {background-image="klondike.jpg" background-opacity="0.5"}
### Slope is critical to movement, so attach heights to nodes and calculate slope in each direction along lattice edges
### Then use a *hiking function* to estimate traversal times

@@

![](fig-betweenness-map-2.png){fig-align="center"}

@@

![](fig-radius-limited-betweenness-2.png){fig-align="center"}

@@

![](fig-betweenness-limited-sites-2.png){fig-align="center"}

@@

![](fig-approx-minimum-arborescence-2.png){fig-align="center"}

# [Conclusions]{style="color:white;"} {.smaller background-image="beacon-valley.jpg" style="color:white;"}

@@

::: {style="text-shadow:0px 0px 8px rgba(102,0,0,0.5),0px 0px 4px rgba(102,0,0,0.65);background-color:rgba(102,0,0,0.1);backdrop-filter:blur(2px);padding:5px;border-radius:5px;"}
### Hiking network concept is implicit in hiking functions but a new terrain representation {style="color:white;"}
### Terrain-differentiated GPS data-fitted hiking functions are novel {.fragment style="color:white;"}
### Potential wider application of radius-limited betweenness centrality {.fragment style="color:white;"}
### Next up: start a conversation with Antarctic scientists about planning {.fragment style="color:white;"}
:::

@@

::: {style="background-color:rgba(102,0,0,0.1);backdrop-filter:blur(2px);padding:5px;border-radius:5px;"}
<h2 style="text-align:center;">For more</h2>
### On this project [dosull.github.io/antarctica](https://dosull.github.io/antarctica) {style="text-align:center;"}
### On ![](logo.png){style="vertical-align:middle;width:60px;text-align:center;"} Geospatial Stuff [dosull.github.io](https://dosull.github.io) {style="text-align:center;"}
:::
